Running faster scripts with DaemonMode.jl

### 2021-10-24 paper/paper.tex
Add files to paper directory.
Fix UTF-8 possible error.

% JuliaCon proceedings template
\documentclass{juliacon}
\usepackage{booktabs}
\usepackage{subcaption}
\setcounter{page}{1}

@@

\begin{lstlisting}
$ jclient bad.jl
ERROR: LoadError: UndefVarError: b not defined
Stacktrace:
  [1] fun2 at .../bad.jl:2
  [2] fun1 at .../bad.jl:6
  [3] top-level scope at .../bad.jl:9 
\end{lstlisting}

@@

The output is nice:
\begin{lstlisting}
$ jclient test_log1.jl
   Warning: warning 1
   another line
   last one
   @ Main /.../test_log1.jl: 4
   Error: error 1
   @ Main /.../test_log1.jl: 5
   Info: info 1
   @ Main /.../test_log1.jl: 6
\end{lstlisting}

@@

\begin{figure}[htp]
  \centering
  \begin{subfigure}[a]{\linewidth}
    \lstinputlisting{../test/hello.jl}
    \caption{\textbf{hello} program}
  \end{subfigure}
  \begin{subfigure}[b]{\linewidth}
    \lstinputlisting{../test/slow.jl}
    \caption{\textbf{slow} program}
  \end{subfigure}
  \begin{subfigure}[c]{\linewidth}
    \lstinputlisting{../test/long.jl}
    \caption{\textbf{long} program, with several output and sleep}
  \end{subfigure}
  \begin{subfigure}[d]{\linewidth}
    \lstinputlisting{../test/DS.jl}
    \caption{\textbf{DS} program, using CSV and DataFrames\vspace{1em}}
  \end{subfigure}
  \caption{Source code of programs used in Section \ref{sec:performance}}
  \label{fig:source_code}
\end{figure}

>>>>

% JuliaCon proceedings template
\documentclass{juliacon}
\usepackage{booktabs}
\usepackage[utf8]{inputenc}
\usepackage{subcaption}
\setcounter{page}{1}

@@

\begin{lstlisting}
$ jclient bad.jl
ERROR: LoadError: UndefVarError: b not defined
Stacktrace:
  [1] fun2 at bad.jl:2
  [2] fun1 at bad.jl:6
  [3] top-level scope at bad.jl:9 
\end{lstlisting}

@@

The output is nice:
\begin{lstlisting}
  $ jclient testlog.jl
  |- Warning: warning 1
  | another line
  | last one
  |- @ Main /.../testlog.jl: 4
  |- Error: error 1
  |- @ Main /.../testlog.jl: 5
  |- Info: info 1
  |- @ Main /../testlog.jl: 6

\end{lstlisting}

@@

\begin{figure}[htp]
  \centering
  \begin{subfigure}[a]{\linewidth}
    \lstinputlisting{hello.jl}
    \caption{\textbf{hello} program}
  \end{subfigure}
  \begin{subfigure}[b]{\linewidth}
    \lstinputlisting{slow.jl}
    \caption{\textbf{slow} program}
  \end{subfigure}
  \begin{subfigure}[c]{\linewidth}
    \lstinputlisting{long.jl}
    \caption{\textbf{long} program, with several output and sleep}
  \end{subfigure}
  \begin{subfigure}[d]{\linewidth}
    \lstinputlisting{DS.jl}
    \caption{\textbf{DS} program, using CSV and DataFrames\vspace{1em}}
  \end{subfigure}
  \caption{Source code of programs used in Section \ref{sec:performance}}
  \label{fig:source_code}
\end{figure}
